\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks = true,
            linkcolor = red,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\hypersetup{pdfborder = 0 0 0}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



\begin{document}

\begin{center}
    {\Huge \scshape Anuar Begenov} \\ \vspace{1pt}
    \small
    \raisebox{-0.1\height}\faPhone\ +7 701 271 8723 ~
    \href{mailto:anuarbegenov111@gmail.com}{\faEnvelope\ anuarbegenov111@gmail.com} ~
    \href{https://www.linkedin.com/in/anuar-begenov-20a9aa204/}{\faLinkedin\ anuar-begenov}  ~
    \href{https://github.com/Anuar111}{\faGithub\ Anuar111}
    \vspace{-8pt}
\end{center}


% -----------Summary-----------
\section{Summary}
  \small{Senior frontend engineer with 5+ years of experience. Currently architecting Bank CenterCredit's operational CRM platform -- a 19-app Nx monorepo used daily by the bank's call-center, sales, and back-office teams. Background spans full-stack Node.js / NestJS systems and Web3 product engineering. I own features end-to-end, lead codebase-wide migrations, and turn sprawling repositories into systems that ship.}
\vspace{-12pt}
% adjust vscape based on the space you want to leave between each section.

%-----------Technical Skills-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, Go, Solidity, Dart, PostgreSQL, MySQL} \\
     \textbf{Frameworks / Libraries}{: React, Next.js, Angular, NestJS, Node.js, Express, Redux Toolkit / RTK Query, react-hook-form, MUI} \\
     \textbf{Tooling \& Infrastructure}{: Nx, Vite, Vitest, Playwright, Storybook, Module Federation, Docker, Kubernetes, GCP, AWS, Firebase, Sentry, Git}\\

    }}
 \end{itemize}
 \vspace{-20pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bank CenterCredit (BCC)}{Sep 2023 -- Present}
      {Senior Frontend Engineer}{Almaty}
      \resumeItemListStart
        \resumeItem{Senior frontend engineer on OCRM-front, the bank's operational CRM; ranked \#1 contributor to the active development branch over the last 24 months on a 19-app Nx monorepo of 3{,}600+ TS files; landed 161 merges to dev, master, pp, and redesign after code review.}
        \resumeItem{Led the Feature-Sliced Design (FSD) monorepo migration -- scaffolded 15 of 19 domain apps and ran the cross-cutting refactor that moved entities, features, widgets, and pages out of a shared library into app-local layers; one migration commit alone touched 1{,}967 files.}
        \resumeItem{Drove the codebase-wide React 19.2 upgrade end-to-end -- eliminated legacy forwardRef in a 44-file single-PR sweep, replaced ad-hoc context with useSyncExternalStore, added useTransition to heavy table sorts, and fixed effect-cleanup leaks across the app.}
        \resumeItem{Cut the main JS bundle to 240 KB and made the chunk-size budget gzip-aware so it reflects real download cost; co-led the broader performance push that shaved another 500 KB via barrel-import elimination, bfcache support, lazy MUI date localization, and deferred analytics.}
        \resumeItem{Rebuilt the Cisco Finesse telephony stack used by the bank's entire call-center -- from a flaky main-thread client into a Web Worker / SharedWorker architecture with XMPP-driven call entities, reconnect logic, and Sentry instrumentation -- then extracted it as a Module Federation microfrontend.}
    \resumeItemListEnd

    \resumeSubheading
      {Sendnomad}{Apr 2023 -- Sep 2023}
      {Full-Stack Developer}{Almaty}
      \resumeItemListStart
        \resumeItem{Built the company's money-transfer web product from the ground up in Next.js while maintaining the existing Flutter mobile app; authored and maintained Firebase Cloud Functions powering both clients.}
        \resumeItem{Rewrote the internal admin panel from scratch in Next.js and shipped A/B experiments backed by user-event funnels and product analytics, while raising the frontend test coverage bar.}
    \resumeItemListEnd

    \resumeSubheading
      {Tech Culture}{Oct 2022 -- Apr 2023}
      {Backend Developer}{Almaty}
      \resumeItemListStart
        \resumeItem{Shipped multiple Web3 products -- an NFT marketplace, a social network, staking apps, and an infrastructure blockchain SaaS -- using NestJS, Express, and Go; deployed services to AWS and DigitalOcean with PM2 and nginx.}
        \resumeItem{Owned diverse backend systems: Redis-backed job queues, JWT cookie auth, gRPC microservices, WebSocket listeners that reflected on-chain events into the database, and cron-based DB-to-chain reconciliation.}
    \resumeItemListEnd

    \resumeSubheading
      {Morre.io / METAFORRA}{Aug 2021 -- Oct 2022}
      {Full-Stack Developer}{Almaty}
      \resumeItemListStart
        \resumeItem{Built and operated a crypto exchange in Express and Angular, including real-time prices and candlestick charts over WebSockets; also maintained a marketplace for local clothing brands with CSV reporting.}
        \resumeItem{Led blockchain engineering for METAFORRA, a Play2Earn game -- drove architectural decisions, authored, tested, and deployed multiple smart contracts, and built DDD-style microservices on NestJS with RabbitMQ.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}
% adjust vscape based on the space you want to leave between each section.

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-6pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{ttfluence} $|$ \emph{Next.js, React 19, NestJS, gRPC, PostgreSQL, Terraform}}{Feb 2024 -- Present}
        \resumeItemListStart
          \resumeItem{Co-founder \& Lead Engineer of a creator-monetization platform connecting TikTok / Threads / Instagram creators with paid campaigns (Telegram mini-app + Refine admin + NestJS backend on PostgreSQL and Render); 1{,}273 personal commits (42\% of team output) across 9 production repositories over 27 months alongside two co-founder engineers.}
          \resumeItem{Built the full stack end-to-end: a NestJS monorepo with one REST core and three gRPC microservices (Apify-based creator verification, Qiwi card payments, TikTok / Threads scraping), a Telegram mini-app frontend (Next.js + React 19 + Tailwind), a Refine + MUI admin dashboard, a 40+ model PostgreSQL schema with 65+ migrations, and Terraform IaC on Render as sole owner.}
          \resumeItem{Owned production-critical workflows: Qiwi card payments with async status rechecks and idempotent refunds, Apify-driven creator verification with BullMQ async follower refresh, an audit + rollback framework with canRollback policy and pre-rollback cleanup hooks, and a 5-tier RBAC (Admin / Operator / Finance / Moderator / User) enforced authoritatively on the backend.}
          \resumeItem{Drove the May 2026 platform consolidation: unified three standalone apps into a pnpm / Turborepo monorepo, scaffolded shared packages (api-types, eslint-config, design-tokens), and coordinated a major-version refresh across the stack (React 19, Next 16, NestJS 11, Tailwind 4, Prisma 6, TypeScript 6).}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kazakh-British Technical University (KBTU), Almaty}{2018 -- 2020}
      {Bachelor of Computer Engineering and Software}{}

      \small{\textbf{Incomplete higher education}}
  \resumeSubHeadingListEnd
\vspace{-18pt}


\end{document}
